Making all equalities equal

### 2021-09-21 paper.lagda.tex
added symmetric equality

@@

>>>>

    module _ {_≣_ : ≣-Type} where
      sym-Equality₂ : (≡-≡-≣ : {x y : A} → let
        x≡y : Type (ℓ-max a ℓ)
        x≡y = x ≡₁ y
        x≣y = x ≣ y
        in x≡y ≡ x≣y)
        → IsEquality₂ _≣_
      sym-Equality₂ ≡-≡-≣ = eq (sym ≡-≡-≣)

@@

      module _ {_≣_ : ≣-Type'} where
        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type (ℓ-max a ℓ)
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y)
          → IsEquality₃ _≣_
        sym-Equality₃ ≡-≡-≣ = eq (let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = transport (sym α₁) ≡-≡-≣
          in transport α₁ (sym α₂))
